Regular singular Volterra equations on complex domains

### 2023-08-31 reg-sing-volterra.tex
Hide verifications

\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{eqnarray}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor} %% for revisions
\usepackage{xparse} %% for squiggly underlines
\usepackage{tikz-cd} %% for term norm scratch work
\usepackage{tikz}

@@

% drafting environments
\newenvironment{verify}{\color{ForestGreen}}{\color{black}}
\newenvironment{brainstorm}{\color{violet}\begin{itemize}}{\end{itemize}\color{black}}

@@

In its most basic form, the Laplace transform $\laplace$ turns exponential-type functions of a real ``position'' variable $\zeta$ into holomorphic\begin{verify}\footnote{\begin{verify}Suppose the magnitude of the Laplace transform integrand is Riemann-integrable on $(0, \infty)$. Write $z$ in terms of its real and imaginary parts as $x + iy$. Since the integrand is holomorphic with respect to $z$, the operator $\frac{\partial}{\partial\overline{z}} = \frac{1}{2}\left(\frac{\partial}{\partial x} + i\frac{\partial}{\partial x}\right)$ annihilates it. Using the comparison version of Leibniz's rule for improper integrals (Theorem~11.10 of A First Course in Real Analysis, by Protter and Morrey) with $\frac{\partial}{\partial x}$ and $\frac{\partial}{\partial y}$, we see that $\frac{\partial}{\partial\overline{z}}$ annihilates the whole integral.\end{verify}}\end{verify} functions of a complex ``frequency'' variable $z$. Through identities like

@@

The kernel of $\volterra^\alpha$ extends meromorphically over all of $\C^2$. One part of this observation demands some explanation: we need to confirm that the power series defining $k_R$ converges everywhere. To do this, recall that $R(z^{-1})$ is holomorphic on the disk $|z| > A$. Consequently, for any $\lambda > A$, we have $|R_{j}| \lesssim \lambda^j$ over all $j \in \{0, 1, 2, \ldots\}$. This is enough to show that $k_R$ is well-defined throughout $\C^2$. In fact, as we'll see later, it also leads to a useful bound on $k_R$.
\begin{verify}
\begin{align*}
& \sum_{j = 0}^\infty R_j z^{-j} \text{ converges when } |z| > A \\
\Longrightarrow & \sum_{j = 0}^\infty R_j z^{-j} \text{ converges when } |z^{-1}| < A^{-1} \\
\Longrightarrow & A^{-1} \le \operatorname{radius} R_j \\
\Longrightarrow & A \ge \big(\operatorname{radius} R_j\big)^{-1} \\
\Longrightarrow & A \ge \limsup_{j \to \infty} R_j^{1/j} \\
\Longrightarrow & A \ge \inf_{J \ge 0} \sup_{j \ge J} R_{r,j}^{1/j} \\
\Longrightarrow & \forall \lambda > A: \exists J: \sup_{j \ge J} R_{r,j}^{1/j} < \lambda \\
\Longrightarrow & \forall \lambda > A: \exists J: \forall j \ge J: R_{r,j}^{1/j} < \lambda \\
\Longrightarrow & \forall \lambda > A: \exists J: \forall j \ge J: R_{r,j} < \lambda^j
\end{align*}
\end{verify}

>>>>

\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{eqnarray}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor} %% for revisions
\usepackage{xparse} %% for squiggly underlines
\usepackage{tikz-cd} %% for term norm scratch work
\usepackage{environ} % to hide verifications
\usepackage{tikz}

@@

% drafting environments
\newenvironment{brainstorm}{\color{violet}\begin{itemize}}{\end{itemize}\color{black}}

% hideable verifications
\newif\ifshowverify
\showverifyfalse
\ifshowverify
\newenvironment{verify}{\color{ForestGreen}}{\color{black}}
\else
\NewEnviron{verify}{\iffalse\expandafter\BODY\fi}
\fi

@@

In its most basic form, the Laplace transform $\laplace$ turns exponential-type functions of a real ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$. \begin{verify}[Suppose the magnitude of the Laplace transform integrand is Riemann-integrable on $(0, \infty)$. Write $z$ in terms of its real and imaginary parts as $x + iy$. Since the integrand is holomorphic with respect to $z$, the operator $\frac{\partial}{\partial\overline{z}} = \frac{1}{2}\left(\frac{\partial}{\partial x} + i\frac{\partial}{\partial x}\right)$ annihilates it. Using the comparison version of Leibniz's rule for improper integrals (Theorem~11.10 of A First Course in Real Analysis, by Protter and Morrey) with $\frac{\partial}{\partial x}$ and $\frac{\partial}{\partial y}$, we see that $\frac{\partial}{\partial\overline{z}}$ annihilates the whole integral.]\end{verify} Through identities like

@@

The kernel of $\volterra^\alpha$ extends meromorphically over all of $\C^2$. One part of this observation demands some explanation: we need to confirm that the power series defining $k_R$ converges everywhere. To do this, recall that $R(z^{-1})$ is holomorphic on the disk $|z| > A$. Consequently, for any $\lambda > A$, we have $|R_{j}| \lesssim \lambda^j$ over all $j \in \{0, 1, 2, \ldots\}$. This is enough to show that $k_R$ is well-defined throughout $\C^2$. As we'll see later, it also leads to a useful bound on $k_R$.
\begin{verify}
\begin{align*}
& \sum_{j = 0}^\infty R_j z^{-j} \text{ converges when } |z| > A \\
\Longrightarrow & \sum_{j = 0}^\infty R_j z^{-j} \text{ converges when } |z^{-1}| < A^{-1} \\
\Longrightarrow & A^{-1} \le \operatorname{radius} R_j \\
\Longrightarrow & A \ge \big(\operatorname{radius} R_j\big)^{-1} \\
\Longrightarrow & A \ge \limsup_{j \to \infty} R_j^{1/j} \\
\Longrightarrow & A \ge \inf_{J \ge 0} \sup_{j \ge J} R_j^{1/j} \\
\Longrightarrow & \forall \lambda > A: \exists J: \sup_{j \ge J} R_j^{1/j} < \lambda \\
\Longrightarrow & \forall \lambda > A: \exists J: \forall j \ge J: R_j^{1/j} < \lambda \\
\Longrightarrow & \forall \lambda > A: \exists J: \forall j \ge J: R_j < \lambda^j
\end{align*}
\end{verify}
